Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
shortened a lot of overly long lines in the latex source
add note

The question of what was meant by ``sustainability'' in the context of software
came up in many different parts of the workshop, specifically in the first
keynote (\S\ref{sec:keynote1}), the Developing and Maintaining Software panel, and the Policy panel.

>>>>

\note{So far this reads a lot like a collection of thoughts only, without ``red line''.}
The question of what was meant by ``sustainability'' in the context of software
came up in many different parts of the workshop, specifically in the first
keynote (\S\ref{sec:keynote1}), the Developing and Maintaining Software panel,
and the Policy panel.
